Exploring the evolution of stellar rotation using Galactic kinematics

### 2020-04-22 paper/ms63.tex
adding orcids and acknowledgements

\author{Ruth Angus}
\affiliation{Department of Astrophysics, American Museum of Natural History,
200 Central Park West, Manhattan, NY, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute,
162 5th Avenue, Manhattan, NY, USA}
\affiliation{Department of Astronomy, Columbia University, Manhattan, NY, USA}

\author[0000-0002-8658-1453]{Angus~Beane}
\affiliation{Center for Astrophysics \textpipe{} Harvard \&
Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}

@@

\author{Travis Berger}
\affiliation{Institute for Astronomy, University of Hawai`i, 2680
Woodlawn Drive, Honolulu, HI 96822, USA}

@@

\author{Rocio Kiman}
\affiliation{Department of physics, CUNY Graduate Center, City
University of New York, Manhattan, NY, USA}

@@

We would like to thank Suzanne Aigrain for providing thoughtful insight that
improved this paper.
This work was partly developed at the 2019 KITP conference `Better stars,
better planets'.
This research was supported in part by the National Science Foundation under
Grant No. NSF PHY-1748958.
Parts of this project are based on ideas explored at the Gaia sprints at the
Flatiron Institute in New York City, 2016 and MPIA, Heidelberg, 2017.
This work made use of the gaia-kepler.fun crossmatch database created by Megan
Bedell.

>>>>

\author[0000-0003-4540-5661]{Ruth Angus}
\affiliation{Department of Astrophysics, American Museum of Natural History,
200 Central Park West, Manhattan, NY, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute,
162 5th Avenue, Manhattan, NY, USA}
\affiliation{Department of Astronomy, Columbia University, Manhattan, NY, USA}

\author[0000-0002-8658-1453]{Angus~Beane}
\affiliation{Center for Astrophysics $\vert$ Harvard \&
Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}

@@

\author[0000-0002-2580-3614]{Travis Berger}
\affiliation{Institute for Astronomy, University of Hawai`i, 2680
Woodlawn Drive, Honolulu, HI 96822, USA}

@@

\author[0000-0003-2102-3159]{Rocio Kiman}
\affiliation{Department of physics, CUNY Graduate Center, City
University of New York, Manhattan, NY, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History,
200 Central Park West, Manhattan, NY, USA}

@@

We thank the anonymous referee for their comments which greatly improved the
manuscript.
We would like to thank Suzanne Aigrain for providing thoughtful insight that
improved this paper.
This work was partly developed at the 2019 KITP conference `Better stars,
better planets'.
This research was supported in part by the National Science Foundation under
Grant No. NSF PHY-1748958.
Parts of this project are based on ideas explored at the Gaia sprints at the
Flatiron Institute in New York City, 2016 and MPIA, Heidelberg, 2017.
This work made use of the gaia-kepler.fun crossmatch database created by Megan
Bedell.
T.A.B. acknowledges support by a NASA FINESST award (80NSSC19K1424).
